---
title: "`r params$prefix` KU Virus Discovery Pipeline Analysis Report"
output: html_document
params:
  version: "v2.0"
---

```{r include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

```{r message=FALSE, warning=FALSE}
library("dplyr")
library("data.table")
library("DT")
```

```{r}
# --- Parsing functions ---
ref_map_to_table <- function(text_file) {
  ret <- read.table(text_file, header = TRUE, sep = "", strip.white = TRUE)
  ret <- select(ret, -c("N_COVERED_BASES", "AVG_BASEQ", "AVG_MAPQ"))
  return(ret)
}

blast_to_table <- function(text_file) {
  ret <- read.table(text_file, header = TRUE, sep = "\t", strip.white = TRUE, quote="", fill = TRUE)
  ret$BITSCORE <- as.integer(ret$BITSCORE)
  ret$TAXID <- as.factor(ret$TAXID)
  ret$superkingdom <- as.factor(ret$superkingdom)
  ret$phylum <- as.factor(ret$phylum)
  ret$class <- as.factor(ret$class)
  ret$order <- as.factor(ret$order)
  ret$family <- as.factor(ret$family)
  ret$genus <- as.factor(ret$genus)
  ret$species <- as.factor(ret$species)
  return(ret)
}

uniq_ref_species <- function(blast_table) {
  ret <- blast_table[order(-blast_table$"BITSCORE"),]
  ret$species <- as.character(ret$species)
  ret <- ret[!duplicated(ret[ , "species"]), ]
  cnt <- as.data.frame(table(blast_table$"species"))
  colnames(cnt) <- c("species", "NUM_CONTIGS")

  ret <- inner_join(ret, cnt, by = "species")
  ret <- ret[c("NUM_CONTIGS", "species", "PER_IDENT", "EVALUE", "BITSCORE")]
  ret <- ret[order(-ret$"BITSCORE"),]
  ret$species <- as.factor(ret$species)
  colnames(ret) <- c("NUM_CONTIGS", "REF_SPECIES", "BEST_PER_IDENT", "BEST_EVALUE", "BEST_BITSCORE")
  return(ret)
}

# --- Input Data ---
prefix <- params$prefix

# QC file
qc_link <- params$qc_link

# reference mapping data
if(file.exists(params$ref_map_summary_file)){
  ref_map_summary_table <- ref_map_to_table(params$ref_map_summary_file)
} else {
  ref_map_summary_table <- data.table()
}

# classification heatmap image files
classification_order_heatmap_file <- paste(params$classification_base_dir_path, "/", prefix, "_order.svg", sep = "")
classification_family_heatmap_file <- paste(params$classification_base_dir_path, "/", prefix, "_family.svg", sep = "")
classification_genus_heatmap_file <- paste(params$classification_base_dir_path, "/", prefix, "_genus.svg", sep = "")
classification_species_heatmap_file <- paste(params$classification_base_dir_path, "/", prefix, "_species.svg", sep = "")

# contigs file
if(file.exists(contigs_len_file)){
  contigs_len <- read.table(params$contigs_len_file, col.names=c("length"))
}
else{
  contigs_len <- vector()
}

# blast data
if(file.exists(params$blast_blastn_file)){
  blast_blastn_table <- blast_to_table(params$blast_blastn_file)
  blast_uniq_blastn_table <- uniq_ref_species(blast_blastn_table)
}
else{
  blast_uniq_blastn_table <- data.frame()
}
if(file.exists(params$blast_megablast_file)){
  blast_megablast_table <- blast_to_table(params$blast_megablast_file)
  blast_uniq_megablast_table <- uniq_ref_species(blast_megablast_table)
}
else{
  blast_uniq_megablast_table <- data.frame()
}
if(file.exists(params$blast_blastx_file)){
  blast_blastx_table <- blast_to_table(params$blast_blastx_file)
  blast_uniq_blastx_table <- uniq_ref_species(blast_blastx_table)
}
else{
  blast_uniq_blastx_table <- data.frame()
}

# subset blast data and save as widgets
table_header_order <- c("superkingdom", "phylum", "class", "order", "family", "genus", "species", "TAXID", "REF_ID", "REF_TITLE", "QUERY_ID", "REF_ID", "EVALUE", "BITSCORE", "PER_IDENT", "QUERY_LEN", "ALN_LEN", "MISMATCH", "GAPOPEN", "QSTART", "QEND", "REFSTART", "REFEND")
if(file.exists(params$blast_blastn_file)){
  blast_blastn_table <- blast_blastn_table[, table_header_order]
  blastn_datatable <- datatable(blast_blastn_table,
                                filter = 'top', 
                                extensions = 'Buttons', 
                                options = list(pageLength = 20,
                                              autoWidth = TRUE,
                                              paging = TRUE,
                                                searching = TRUE,
                                                fixedColumns = TRUE,
                                                ordering = TRUE,
                                                dom = 'tB',
                                                buttons = c('copy', 'csv', 'excel')),
                                class = 'display')
  blastn_html_link <- paste("analysis/", prefix, ".full_blastn_table.html", sep = "")
  saveWidget(blastn_datatable, paste(getwd(),"/",prefix,"/",blastn_html_link, sep=""))
}
else{
  blastn_html_link <- ""
}
if(file.exists(params$blast_megablast_file)){
  blast_megablast_table <- blast_megablast_table[, table_header_order]
  megablast_datatable <- datatable(blast_megablast_table, 
                                  filter = 'top', 
                                  extensions = 'Buttons', 
                                  options = list(pageLength = 20,
                                                  autoWidth = TRUE,
                                                  paging = TRUE,
                                                  searching = TRUE,
                                                  fixedColumns = TRUE,
                                                  ordering = TRUE,
                                                  dom = 'tB',
                                                  buttons = c('copy', 'csv', 'excel')),
                                  class = 'display')
  megablast_html_link <- paste("analysis/", prefix, ".full_megablast_table.html", sep = "")
  saveWidget(megablast_datatable, paste(getwd(),"/",prefix,"/", megablast_html_link, sep=""))
}
else{
  megablast_html_link <- ""
}
if(file.exists(params$blast_blastx_file)){
  blast_blastx_table <- blast_blastx_table[, table_header_order]
  blastx_datatable <- datatable(blast_blastx_table,
                                filter = 'top', 
                                extensions = 'Buttons', 
                                options = list(pageLength = 20,
                                              autoWidth = TRUE,
                                              paging = TRUE,
                                                searching = TRUE,
                                                fixedColumns = TRUE,
                                                ordering = TRUE,
                                                dom = 'tB',
                                                buttons = c('copy', 'csv', 'excel')),
                                class = 'display')
  blastx_html_link <- paste("analysis/", prefix, ".full_blastx_table.html", sep = "")
  saveWidget(blastx_datatable, paste(getwd(),"/",prefix,"/", blastx_html_link, sep=""))
}
else{
  blastx_html_link <- ""
}
```

A report that displays the results generated from KU Virus Discovery Pipeline `r params$version`.

This report contains the analysis result of the Nanopore sequencing throughput originated from the sample named **`r prefix`**.

## Results
### QC

QC result of the given input fastq file. The independent report produced with NanoPlot is linked [here](`r qc_link`).

### Reference Mapping
```{r}
knitr::kable(ref_map_summary_table, caption = 'Column follows bamcov format.')
```

### Read classification
```{r, fig.align='center', fig.cap='Order-level heatmap'}
knitr::include_graphics(classification_order_heatmap_file)
```
```{r, fig.align='center', fig.cap='Family-level heatmap'}
knitr::include_graphics(classification_family_heatmap_file)
```
```{r, fig.align='center', fig.cap='Genus-level heatmap'}
knitr::include_graphics(classification_genus_heatmap_file)
```
```{r, fig.align='center', fig.cap='Species-level heatmap'}
knitr::include_graphics(classification_species_heatmap_file)
```

The piechart generated from Kraken result is linked [here](`r classification_kraken_link`).

The piechart generated from Kaiju result is linked [here](`r classification_kaiju_link`).

### Assembly
```{r}
ggplot(contigs_len, aes(x=length))+
  geom_histogram(color="darkblue", fill="lightblue") + 
  geom_vline(aes(xintercept=mean(length)),
            color="blue", linetype="dashed", size=1)
```

The histogram shows the length distribution of the assembled contigs. Dashed line indicates the mean length of them.

### Contigs analysis
#### BLAST
##### BLASTn
```{r}
knitr::kable(blast_uniq_blastn_table)
```
More functional table is linked [here](`r blastn_html_link`).

##### megaBLAST
```{r}
knitr::kable(blast_uniq_megablast_table)
```
More functional table is linked [here](`r megablast_html_link`).

##### Diamond(BLASTx)
```{r}
knitr::kable(blast_uniq_blastx_table)
```
More functional table is linked [here](`r blastx_html_link`).

#### Zoonotic Rank
